---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# richcleaner

<!-- badges: start -->

[![](https://img.shields.io/badge/devel%20version-0.0.0.9-blue.svg)](https://github.com/c1au6i0/richcleaner)

<!-- badges: end -->

The goal of `{richcleaner}` is to clean up enriched data generated by [gsea](https://www.gsea-msigdb.org/gsea/index.jsp). Just a couple of handy functions that we can share in Marchionni lab.

The package as it is right now works **only on `unix` systems**.

## Installation

``` r
library(devtools)

devtools::install_github("c1au6i0/richcleaner")
```
## Preparation of folders

Organize the folders in contrasts, each containing one the folder for each of the gene set databases used in `gsea`. Put the whole `gsea` output folder in the corresponding section. 


```{r, echo=FALSE}
setwd("inst")
library(fs)
dir_tree("root_folder")
```

## Aggregation

Use the function `rich_aggregate` to look inside that tree folder for `reports files` and to aggregate them in a single long dataframe. Running the function with no `path` argument starts an interactive `{svDialogs}` modal dialog box to choose the folder.

``` r
library(richcleaner)
rich_results <- rich_aggregate()
names(rich_results)
```
```{r, echo=FALSE}
c("contrast", "gs", "description", "size", "es", "nes", "nom_p_val", 
"fdr_q_val", "fwer_p_val", "rank_at_max", "leading_edge")
```


Some packages like `{pheatmaps}` takes as an input a matrix, so it is convenient to select the results of a particular gene set database and to pivot the dataframe in a wider format with `rich_wider`.

``` r
rich_results_wider <- rich_wider(rich_results, fdr_threshold = 0.001, gs = "GOBPs", value = "n_logp_sign")
```

The argument `fdr_threshold` is used for filtering out gene sets that have an false discovery rate more than a certain number. We can pivot wider the dataframe setting `value` to one of the numerical columns of the dataframe.

## Plotting

The function `rich_pheatmap` is just a wrapper than runs `rich_wider` and `pheatmap::pheatmap` on the result.



